Country-Level Impact of Education on Entrepreneurship

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

Still, if we look at the following data from the [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org) Adult Population Survey (APS) from 2012, there seem to be different amounts of entrepreneurial self-efficacy between countries. By a country's entrepreneurial self-efficacy we mean the belief that the average individual of that country holds about his or her abilities to succeed as an entrepreneur. Here, the variable "perceived capabilites" has to be understood in a narrow sense, it refers only to the perceived capabilities to start a business. Seemingly the variable "fear of failure" only refers to the fear of failure as an obstacle in starting a business, despite the perceived good opportunities.

@@

Specifically, we expect to find out to what extent positive reinforcement in teaching can impact the rate of entrepreneurship at a country level, especially across OECD countries. Indeed, regarding France and the United Kingdom, many parameters differ between the two education systems but one stands out, that is the positive reinforcement. Indeed, while positive reinforcement is effectively in use throughout the compulsory education system in the UK, it is much more rarely activitated in France, and only on an voluntary individual teacher's basis. Drawing from Inglehart research ????????? MAIN BIB 2000 ????????, we understand the period between 0 and 20 years of age to be a defining time in terms of personal values and personality construction, thus compulsory education, generally between 6 and 16 years of age, can prove of key importance in the building up of one's self-confidence. We would like to verify if this has to do with the amount of entrepreneurial self-efficacy mentioned above, in which case this could also affect entrepreneurial intentions, behaviours and actions.

This assumption draws from Boyd and Vozikis's ??????? MAIN BIB ???????? stating how entrepreneurial intentions are at least partially the result of thought processes, which "underlie the creation of formal business plans, opportunity analysis, and goal-directed behaviour". Boyd and Vosikis also assert that individual self-efficacy "influences the development of both entrepreneurial intentions and actions or behaviours". To assert this, they rely on Fishbein and Ajzen 1975 ?????? MAIN BIB ???????? who illustrate the relation between beliefs and behaviour as follows:

>>>>

Still, if we look at the following data from the [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org) Adult Population Survey (APS) from 2012, there seem to be different amounts of self-confidence and entrepreneurial self-efficacy between countries. By a country's entrepreneurial self-efficacy we mean the belief that the average individual of that country holds about his or her abilities to succeed as an entrepreneur. Here, the variable "perceived capabilites" has to be understood in a narrow sense, it refers only to the perceived capabilities to start a business. Seemingly the variable "fear of failure" only refers to the fear of failure as an obstacle in starting a business, despite the perceived good opportunities.

@@

Specifically, we expect to find out to what extent positive reinforcement in teaching can impact the rate of entrepreneurship at a country level, especially across OECD countries. Indeed, regarding France and the United Kingdom, many parameters differ between the two education systems but one stands out, that is the positive reinforcement. Indeed, while positive reinforcement is effectively in use throughout the compulsory education system in the UK, it is much more rarely activitated in France, and only on an voluntary individual teacher's basis.

Drawing from Inglehart research ????????? MAIN BIB 2000 ????????, we understand the period between 0 and 20 years of age to be a defining time in terms of personal values and personality construction, thus compulsory education, generally between 6 and 16 years of age, can prove of key importance in the building up of one's self-confidence. We would like to verify if this has to do with the amount of entrepreneurial self-efficacy mentioned above, in which case this could also affect entrepreneurial intentions, behaviours and actions. This assumption draws from Boyd and Vozikis's ??????? MAIN BIB ???????? stating how entrepreneurial intentions are at least partially the result of thought processes, which "underlie the creation of formal business plans, opportunity analysis, and goal-directed behaviour". Boyd and Vosikis also assert that individual self-efficacy "influences the development of both entrepreneurial intentions and actions or behaviours". To assert this, they rely on Fishbein and Ajzen 1975 ?????? MAIN BIB ???????? who illustrate the relation between beliefs and behaviour as follows:
